\hypertarget{index_intro_sec}{}\section{Introduction\+:}\label{index_intro_sec}
the project is about building transit simulation. The program can be obtain in github \href{https://github.umn.edu/umn-csci-3081-s20/csci3081-shared-upstream/tree/support-code/labs/lab09_project_intro}{\tt https\+://github.\+umn.\+edu/umn-\/csci-\/3081-\/s20/csci3081-\/shared-\/upstream/tree/support-\/code/labs/lab09\+\_\+project\+\_\+intro} using git pull command to obtain the project into local machine, the configure of mechine list below\+: Server\+: Dell Power\+Edge R210 Processor\+: Quad-\/\+Core Intel® Xeon™ E3-\/1220\+V2 Processor @ 3.\+10\+G\+Hz Memory\+: 16\+GB R\+AM with linux system.

the program is execuated by following step\+: Step by step for instructions for C\+SE Labs machines or vole users $<$port\+\_\+number$>$ below should be a number above 8000 that includes the last 3 digits of your student id. So, if your student id number is\+: 1459345, use 8345, or 9345

Navigate to base project directory(project/) Make and run the server\+: \$ cd src \$ make \$ cd .. \$./build/bin/vis\+\_\+sim $<$port\+\_\+number$>$ You must run by doing ./build/bin/vis\+\_\+sim $<$port\+\_\+number$>$. You cannot cd to bin/ and run ./vis\+\_\+sim $<$port\+\_\+number$>$ Run your browser on vole or C\+SE Labs machine, and enter following address in the address bar of your browser (Firefox/\+Chrome)\+: \href{http://127.0.0.1:}{\tt http\+://127.\+0.\+0.\+1\+:}$<$port\+\_\+number$>$/web\+\_\+graphics/project.html Step by step instructions for ssh users \+:

You can S\+SH using a Windows machine with Git Bash.

$\ast$$\ast$$<$port\+\_\+number$>$ below should be a number above 8000 that includes the last 3 digits of your student id.$\ast$$\ast$ {\bfseries So, if your student id number is\+: 1459345, use 8345, or 9345}

ssh -\/L $<$port number$>$=\char`\"{}\char`\"{}$>$\+:127.\+0.\+0.\+1\+:$<$port\+\_\+number$>$ $<$x500$>$$<$cse\+\_\+labs\+\_\+computer$>$.cselabs.\+umn.\+edu Navigate to base project directory(project/) make and start server\+: \$ cd src \$ make \$ cd .. \$./build/bin/vis\+\_\+sim $<$port\+\_\+number$>$ You must run by doing ./build/bin/vis\+\_\+sim $<$port\+\_\+number$>$. You cannot cd to bin/ and run ./vis\+\_\+sim $<$port\+\_\+number$>$ Navigate to the following address into the address bar of a browser (Firefox/\+Chrome) running on your L\+O\+C\+AL machine (e.\+g, your PC)\+: \href{http://127.0.0.1:}{\tt http\+://127.\+0.\+0.\+1\+:}$<$port\+\_\+number$>$/web\+\_\+graphics/project.html

program can be compile by\+: \$ cd src \$ make

the program can be viewed by browser after execuated\+: After running command above, open browser and type in the U\+RL shows above. After browser window opened, prass start batton to start transit simulator

The major improvement in iteration 1 is adding new class bus factory. The main functionality of bus factory is randomly generate 3 kinds of bus which are small, regular, large. To implement the bus factory, I first create smallbus, regularbus and largebus classes that inhirent from \hyperlink{classBus}{Bus} class. There are two way to implement bus factory which are concrete class and abstract class An abstract class is declared using abstract modifier. Concrete class should not be declared using abstract keyword, on doing so, it will also become an abstract class. Instantiation\+: An abstract class cannot be instantiated directly, i.\+e. object of such class cannot be created directly using new keyword. An abstract class can be instantiated either by a concrete subclass or by defining all the abstract method along with the new statement. A concrete class can be instantiated directly, using a new keyword. A concrete class is an ordinary class which has no purely virtual functions and hence can be instantiated. It is main reason why I choose concrete class in this project. I believe that concrete make furture edition of the project more easier 